Object-oriented implementations of the MPDATA advection equation solver in~C++,~Python~and~Fortran

### 2013-03-20 paper/doc/paper.tex
adding CPC Program Summary

%%%%%\documentclass[review,peprint,10pt,5p,times]{elsarticle}
%%%%%\usepackage[switch]{lineno}
%%%%%\addtolength{\hoffset}{.5cm}

\documentclass[final,5p,times,twocolumn]{elsarticle}

@@

@@

%%%%%  \linenumbers % for the review

%%%%%  \section*{Program summary}

%%%%%  \noindent
%%%%%  Program title: mpdata-oop\\
%%%%%  Licensing provisions: GNU GPL version 3 \citep{GPLv3}\\
%%%%%  Programming language: C++11, Python and Fortran 2008\\
%%%%%  External routines/libraries used: Blitz++, NumPy\\
%%%%%  Nature of problem: advective transport\\
%%%%%  Solution method: MPDATA\\
%%%%%  References: Smolarkiewicz 1984: A fully multidimensional positive definite advection transport algorithm with small implicit diffusion. J. Comp. Phys. 54, 325--362 \citep{Smolarkiewicz_1984}

@@

%%%%%%
  \clearpage
%%%%%%
  \appendix

>>>>

%%%%% <cpc>
\documentclass[review,peprint,10pt,5p,times]{elsarticle}
\usepackage[switch]{lineno}
\addtolength{\hoffset}{.5cm}
%%%%% </cpc>

%%%%% <arXiv>
%\documentclass[final,5p,times,twocolumn]{elsarticle}
%%%%% </arXiv>

@@

%%%%% <cpc>
\linenumbers % for the review
\section*{Program summary}
\noindent
{\it Program title:} mpdata-oop\\
{\it Licensing provisions:} GNU GPL version 3\\
{\it Programming languages:} C++, Python and Fortran\\
{\it Computer:} hardware-independent (tested on x86\_64)\\
{\it Operating system:} OS-independent (developed on GNU/Linux)\\
{\it RAM/CPU time requirements:} problem-dependent\\
{\it Has the code been vectorised or parallelised?:}\\ 
  GCC 4.8 auto-vectorises parts of the Fortran and the C++ code.\\
  The code is readily adaptable for concurrent computation using
  domain decomposition.\\
{\it External libraries used:} Blitz++, NumPy\\
{\it Classification:} 70 (Mathematical and Numerical Methods)\\
{\it Nature of problem:} advective transport\\
{\it Solution method:} Multidimensional Positive Definite Advective Transport Algorithm (MPDATA)\\
{\it Reference:} Smolarkiewicz 1984, J. Comp. Phys. 54, 325--362
%%%%% </cpc>

@@

@@

%%%%%% <arXiv>
%  \clearpage
%%%%%% </arXiv>
  \appendix
